%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\graphicspath{Figures/}  % Location of the graphics files (set up for graphics to be in PDF format)

% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.

%% ----------------------------------------------------------------
\begin{document}
\frontmatter      % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title {Techniques for Correlation and Visualization of Telemetry Dependence Relationships for Root Cause Fault Analysis in Complex Systems}
\authors  {\texorpdfstring
            {\href{natguy@uw.edu}{Nathaniel Guy}}
            {Nathaniel Guy}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{

\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I, NATHANIEL GUY, declare that this thesis titled, `TECHNIQUES FOR CORRELATION AND VISUALIZATION OF TELEMETRY DEPENDENCE RELATIONSHIPS FOR ROOT CAUSE FAULT ANALYSIS IN COMPLEX SYSTEMS' and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item[\tiny{$\blacksquare$}] This work was done wholly or mainly while in candidature for a research degree at this University.
 
\item[\tiny{$\blacksquare$}] Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
 
\item[\tiny{$\blacksquare$}] Where I have consulted the published work of others, this is always clearly attributed.
 
\item[\tiny{$\blacksquare$}] Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
 
\item[\tiny{$\blacksquare$}] I have acknowledged all main sources of help.
 
\item[\tiny{$\blacksquare$}] Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.
\\
\end{itemize}
 
 
Signed:\\
\rule[1em]{25em}{0.5pt}  % This prints a line for the signature
 
Date:\\
\rule[1em]{25em}{0.5pt}  % This prints a line to write the date
}
\clearpage  % Declaration ended, now start a new page

%% ----------------------------------------------------------------
% The "Funny Quote Page"
\pagestyle{empty}  % No headers or footers for the following pages

\null\vfill
% Now comes the "Funny Quote", written in italics
\textit{``Okay, 13. We've got lots and lots of people working on this; we'll give you some dope as soon
as we have it, and you'll be the first one to know.'}

\begin{flushright}
Jack Lousma, Apollo 13 CapCom \cite{apollo13}
\end{flushright}

\vfill\vfill\vfill\vfill\vfill\vfill\null
\clearpage  % Funny Quote page ended, start a new page
%% ----------------------------------------------------------------

% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

This thesis explores new ways of looking at telemetry data, from a time-correlative perspective, in order to see patterns within the data that may suggest root causes of system faults. It was thought initially that visualizing an animated Pearson Correlation Coefficient (PCC) matrix for telemetry channels would be sufficient to give new understanding; however, testing showed that the high dimensionality and inability to easily look at change over time in this approach impeded understanding. Principal component analysis (PCA) was used to reduce dimensionality, and the time curve visualization proposed by Bach et al (2015) was adapted to visualize both raw telemetry and telemetry data correlations. Subsequent testing revealed insights into understanding and an intuitive grasp of data families that suggests the viability of this approach to enhance root cause analysis for actual aerospace systems.

}

\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

I would like to thank my advisor, Dr. Mehran Mesbahi, for his academic guidance, his patience, and his constant encouragement as I struggled with the process of determining my own interests in this field. Deep thanks go to Dr. Jeff Heer for his insights and suggestions into the best practices for visualizing the hidden patterns within correlation data. My sincere thanks to Dr. Chris Lum for his opinions and suggestions about aerospace fault detection systems. I'd also like thank my various internship teams for their guidance and encouragement: the JPL OpsLab team, specifically Scott Davidoff, Jeff Norris, and Garrett Johnson, for introducing me to teleoperation interface design and testing techniques with the Unity 3D game engine; the SpaceX Flight Software team, specifically Mike Soares, Dan Gelband and Derek Bronish, for introducing me to Fault Detection, Isolation and Recovery systems and teaching me much about aerospace ground software systems; and the HAKUTO Lunar XPRIZE team, specifically Dr. Nathan Britton, Louis Burtz, Kurai Shimizu, Toshiro Shimizu, Toshiki Tanaka, Dr. John Walker, and Dr. Kazuya Yoshida for letting me use their lunar rover as a testbed for new ground software design methodologies and fault diagnosis techniques. Special thanks go to Daisuke Kikuchi for countless bits of design advice and for helping to increase the aesthetic appeal of the HAKUTO rover ground station UI. My thanks to the team at Unity, for developing an excellent and adaptive game engine. Finally, I'd like to thank Steve Rabin at Nintendo of America for his advice about fault detection and valuable comparisons to runtime analysis and profiling of executable code. Without the aforementioned people and many others, I would be lost!

}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{fancy}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back


%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
\clearpage  % Start a new page
\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
\textbf{FD} & \textbf{F}ault \textbf{D}etection \\
\textbf{FDIR} & \textbf{F}ault \textbf{D}etection, \textbf{I}solation, and \textbf{R}ecovery \\
\textbf{GSN} & \textbf{G}round \textbf{S}tatio\textbf{n} \\
\textbf{PCC} & \textbf{P}earson \textbf{C}orrelation \textbf{C}oefficient \\

}

%% ----------------------------------------------------------------
\clearpage  % Start a new page
\lhead{\emph{Physical Constants}}  % Set the left side page header to "Physical Constants"
\listofconstants{lrcl}  % Include a list of Physical Constants (a four column table)
{
% Constant Name & Symbol & = & Constant Value (with units) \\
Speed of Light & $c$ & $=$ & $2.997\ 924\ 58\times10^{8}\ \mbox{ms}^{-\mbox{s}}$ (exact)\\

}

%% ----------------------------------------------------------------
\clearpage  %Start a new page
\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
\listofnomenclature{lll}  % Include a list of Symbols (a three column table)
{
% symbol & name & unit \\
$\sigma_{X}$ & standard deviation of vector $X$ &  \\

& & \\ % Gap to separate the Roman symbols from the Greek
%$\omega$ & angular frequency & rads$^{-1}$ \\
}
%% ----------------------------------------------------------------
% End of the preamble, contents and lists of things
% Begin the Dedication page

\setstretch{1.3}  % Return the line spacing back to 1.3
\lhead{}  % Clears the left side page header

\pagestyle{empty}  % Page style needs to be empty for this page
\dedicatory{For Carl, who showed me the way to space.}

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics


%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\input{Chapters/Chapter1} % Introduction

\input{Chapters/Chapter2} % Background in Fault Detection, Isolation and Recovery

\input{Chapters/Chapter3} % Correlative Analysis

\input{Chapters/Chapter4} % Visualization of Correlative Relationships

\input{Chapters/Chapter5} % Case Study: Hakuto ``Moonraker" Lunar Rover

\input{Chapters/Chapter6} % Intermediate Results and Reassessment

\input{Chapters/Chapter7} % Dimensional Reduction and Visualization Improvements

\input{Chapters/Chapter8} % Results and Discussion

\input{Chapters/Chapter9} % Conclusion

%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices

\input{Appendices/AppendixA}	% Appendix Title

%\input{Appendices/AppendixB} % Appendix Title

%\input{Appendices/AppendixC} % Appendix Title

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter

%% ----------------------------------------------------------------

\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
\bibliographystyle{plain}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\bibliography{bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"

\end{document}  % The End
%% ----------------------------------------------------------------